---
title: "Untitled"
author: "Ender Alexandru, Laura Fetz, Jessee Moomey"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
# Loading packages
library(cowplot)
library(plotly)
library(gridExtra)
library(tidyverse)
library(devtools)
library(oefenwebDatabase)
library(oefenwebTools)
library(lme4)
library(lmerTest)
library(lubridate)
library(DBI)
library(ggalluvial)
# Establishing connection with oefenweb
con <- oefenwebDatabase::connect()
```

Grab the data from original database

```{r}
# Create necessary objects
ed_logs <- list()
domains <- c(1:5, 7, 9, 10, 11, 59)
change_date <- as.Date("2024-10-25")
start_date <- as.Date("2023-09-01")

# Loop through each E_D table
for (i in 1:10) {
  # Write SQL query to get data, and convert to seconds
  query <- paste0("SELECT *
                   FROM extended_deadline_logs_", domains[i])
  # Get the data and store it in the list
  ed_logs[[i]] <- suppressWarnings(DBI::dbGetQuery(con, query))
}

# Turn the list into a single df
ed_logs <- bind_rows(ed_logs)

# Getting deadlines for items in 59
query <- paste0("SELECT id AS item_id,
                 maximum_response_in_seconds AS deadline
                 FROM extended_deadline_items
                 WHERE domain_id = 59")
  # Get the data and store it in the list
deadlines_59 <- suppressWarnings(DBI::dbGetQuery(con, query))

# Convert created to date and into POSIXct format
ed_logs <- ed_logs %>%
  rename(date = created) 
ed_logs$date <-
  as.POSIXct(ed_logs$date, format = "%Y-%m-%d %H:%M:%S")
```


Ender: analyzing growth slopes in the first 2 months of 2024 (Sep-Oct 25) to growth slopes after the change (Oct 25 - Dec)

```{r}
### Checking amount of items played in the two periods, per domain ###
items_played <- ed_logs %>%
  mutate(period = case_when(
    date > "2024-09-01 00:00:01" & date < "2024-10-25 00:00:01" ~ "Sep-Oct",
    date > "2024-10-25 23:59:59" ~ "Oct-Dec",
    TRUE ~ "other")) %>%
  group_by(domain_id, period) %>%
  summarize(items_played = n()) %>%
  filter(period != "other") %>%
  arrange(domain_id, desc(period))

items_played$period <- factor(items_played$period, levels = c("Sep-Oct", "Oct-Dec"))

items_played %>%
  ggplot(aes(x = domain_id, y = items_played, fill = period)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Items Played by Domain and Period", x = "Domain", y = "Items Played") +
  scale_fill_manual(values = c("Sep-Oct" = "#57b0b5", "Oct-Dec"= "#fe6c66")) +
  custom_theme
```

Having similar (and sufficient) amounts of items played in the two periods across domains, we can proceed with data preparation for a multilevel analysis that investigates growth, taking into account domains, grades, usage of extended deadline


```{r}
### Structuring data for multilevel analysis
period_logs <- ed_logs %>%
  mutate(period = case_when(
    date > "2024-09-01 00:00:01" & date < "2024-10-25 00:00:01" ~ "Sep-Oct",
    date > "2024-10-25 23:59:59" ~ "Oct-Dec",
    TRUE ~ "other")) %>%
  filter(period != "other") %>%
  filter(!is.na(new_user_domain_q_score))

# Record answers as either being in the extended deadline time or not
period_logs <- period_logs %>%
  mutate(late_response = ifelse(response_in_seconds > deadline & answer != "…", 1, 0))
```

```{r}
# Structure data to have a Q-score for every session entry, prepare other variables

# Categorize users that never used, or used extended deadline above or below mean (per domain)
ext_deadline_usage <- period_logs %>%
  group_by(user_id, period, domain_id) %>%
  summarize(
    usage_extended_deadline = mean(late_response),
    never_used_deadline = all(late_response == 0), 
    .groups = "drop") %>%
  ungroup() %>%
  # Calculate the mean usage for each domain (taking into account the period)
  group_by(period, domain_id) %>%
  mutate(
    domain_avg_extended_deadline = mean(usage_extended_deadline[!never_used_deadline])
  ) %>%
  ungroup() %>%
  # Classify users based on domain-specific average
  mutate(
    extended_deadline_group = case_when(
      never_used_deadline ~ "Never",
      usage_extended_deadline > domain_avg_extended_deadline ~ "Above average",
      TRUE ~ "Below average"))

# Compute Q_score at the end of the session, and usage of extended deadline
multilevel_data <- period_logs %>%
  arrange(user_id, period, domain_id, new_user_domain_session_count, new_user_domain_modified_count) %>%
  group_by(user_id, period, domain_id, new_user_domain_session_count) %>%
  # calculate q_score at the end of the session
  summarize(q_score = last(new_user_domain_q_score),
            ext_deadline_usage = mean(late_response), .groups = "drop") %>%
  # need to re-attach grade & difficulty to data
  left_join(period_logs %>%
              select(user_id, period, grade, domain_id, difficulty, new_user_domain_session_count,
                     new_user_domain_modified_count),
            by = c("user_id", "period", "domain_id", "new_user_domain_session_count"))

# Re-number sessions to start from 1 (separate for each period, domain, and user combination)
multilevel_data_unique <- multilevel_data %>%
  distinct(user_id, period, domain_id, new_user_domain_session_count, .keep_all = TRUE) %>%
  group_by(user_id, period, domain_id) %>%
  mutate(session = row_number()) %>%
  ungroup() %>%
  select(-new_user_domain_modified_count, -new_user_domain_session_count)

# Add variable describing category of user (never used, above or below average use of extended deadline)
multilevel_data_unique <- multilevel_data_unique %>%
  left_join(
    ext_deadline_usage %>% 
      select(user_id, period, domain_id, extended_deadline_group),
    by = c("user_id", "period", "domain_id")) %>%
  mutate(extended_deadline_group = relevel(factor(extended_deadline_group), ref = "Never"))

# Check observation numbers per grade, domain
print("Number of sessions for each grade")
table(multilevel_data_unique$grade)
print("Number of sessions for each domain")
table(multilevel_data_unique$domain_id)

# Remove data for grades 1, 2, and 9-19, as there is too little data there
multilevel_data_unique$grade <- as.integer(multilevel_data_unique$grade)
multilevel_data_unique <- multilevel_data_unique %>%
  filter(!(grade == 1) & !(grade == 2) & !(grade >= 9 & grade <= 19))

# Set variables as factors
multilevel_data_unique$difficulty <- as.factor(multilevel_data_unique$difficulty)
multilevel_data_unique$period <- as.factor(multilevel_data_unique$period)
multilevel_data_unique$domain_id <- as.factor(multilevel_data_unique$domain_id)
multilevel_data_unique$grade <- as.factor(multilevel_data_unique$grade)
multilevel_data_unique$extended_deadline_group <- as.factor(multilevel_data_unique$extended_deadline_group)

# Remove sessions over 20; analysis will be done on growth across 20 sessions,
# since there is little data for users that played more than that, and it is noisy
multilevel_data_unique <- multilevel_data_unique %>%
  filter(session <= 20)

# Scale session, q_score; this fixes convergence issues in the models
# analysis results are the same with q_score scaled per domain, or across all domains
# here we scale it across all domains
multilevel_data_unique <- multilevel_data_unique %>%
  mutate(session_scaled = scale(session)) %>%
  mutate(q_score_scaled = scale(q_score)) %>%
  ungroup()

# Extract scaling parameters; will be necessary for plots
session_mean <- attr(scale(multilevel_data_unique$session), "scaled:center")
session_sd <- attr(scale(multilevel_data_unique$session), "scaled:scale")
q_score_mean <- attr(scale(multilevel_data_unique$q_score), "scaled:center")
q_score_sd <- attr(scale(multilevel_data_unique$q_score), "scaled:scale")

# For the analyses we will use multilevel_data_unique as the main data-set
```

```{r}
### T-test to check whether q_score penalty is the same, given that an answer was correct VS incorrect in the extended deadline ###
t_test_data <- period_logs[period_logs$period == "Oct-Dec",] %>%
  group_by(user_id, domain_id) %>%
  mutate(q_score_diff = new_user_domain_q_score - lag(new_user_domain_q_score)) %>%
  mutate(q_score_diff = replace(q_score_diff, is.na(q_score_diff), 0)) %>%  # replace NA with 0
  ungroup()

# group 0 = used extended deadline, responded incorrect
# group 1 = used extended deadline, responded correct
group_0 <- experiment$q_score_diff[experiment$late_response == 1 & experiment$correct_answered == 0]
group_1 <- experiment$q_score_diff[experiment$late_response == 1 & experiment$correct_answered == 1]

# T-test: do players lose the same amount of q_score if they answered correctly VS incorrectly in the extended deadline?
t_test_result <- t.test(group_0, group_1)
print(t_test_result)

# Answer: players lose about 2 more q_score points if they answer incorrectly
```

```{r}
### Multilevel Analyses ###
# Models were tested sequentially; intervention_final fits best
fixed_slopes <- lmer(
  q_score_scaled ~ 1 + session_scaled +
    (1 | user_id),
  REML = F, data = multilevel_data_unique)

random_slopes <- lmer(
  q_score_scaled ~ 1 + session_scaled +
    (1 + session_scaled | user_id),
  REML = F, data = multilevel_data_unique)

domain <- lmer(
  q_score_scaled ~ 1 + session_scaled +
    domain_id +
    (1 + session_scaled | user_id),
  REML = F, data = multilevel_data_unique)

grade <- lmer(
  q_score_scaled ~ 1 + session_scaled +
    domain_id +
    grade +
    (1 + session_scaled | user_id),
  REML = F, data = multilevel_data_unique)
# does not converge with session:grade

difficulty <- lmer(
  q_score_scaled ~ 1 + session_scaled:difficulty +
    domain_id +
    grade +
    (1 + session_scaled | user_id),
  control = lmerControl(optCtrl = list(maxfun = 10000)), # increase iterations to achieve convergence
  data = multilevel_data_unique)
# does not converge with main effect of difficulty
# this is because changes in difficulty do not reset session counter

diff_domain_grade <- lmer(
  q_score_scaled ~ 1 + session_scaled:difficulty +
    domain_id +
    grade +
    session_scaled:domain_id +
    session_scaled:grade +
    (1 + session_scaled | user_id),
  control = lmerControl(optCtrl = list(maxfun = 10000)),
  data = multilevel_data_unique)
# best to include grade & domain main effects, but also growth interactions

intervention_1 <- lmer(
  q_score_scaled ~ 1 + session_scaled*period +
    session_scaled:difficulty +
    domain_id +
    grade +
    session_scaled:domain_id +
    session_scaled:grade +
    (1 + session_scaled | user_id),
  control = lmerControl(optCtrl = list(maxfun = 10000)),
  data = multilevel_data_unique)
# added intervention term (period)

intervention_2 <- lmer(
  q_score_scaled ~ 1 + session_scaled*period +
    session_scaled:difficulty +
    domain_id +
    grade +
    session_scaled:domain_id:period +
    session_scaled:grade:period +
    (1 + session_scaled | user_id),
  control = lmerControl(optCtrl = list(maxfun = 10000)),
  data = multilevel_data_unique)
# added interactions between domains & grades with the period
# this is to account for different slopes between grades and domains, when comparing periods
# fit is good

intervention_3 <- lmer(
  q_score_scaled ~ 1 + session_scaled*period +
    session_scaled:difficulty +
    session_scaled:period:ext_deadline_usage +
    domain_id +
    grade +
    session_scaled:domain_id:period +
    session_scaled:grade:period +
    (1 + session_scaled | user_id),
  control = lmerControl(optCtrl = list(maxfun = 10000)),
  data = multilevel_data_unique)
# does not converge;
# adding growth interaction between user-specific usage of extended deadline & period adds these issues
  
intervention_4 <- lmer(
  q_score_scaled ~ 1 + session_scaled*period +
    session_scaled:difficulty +
    period:extended_deadline_group +
    domain_id +
    grade + 
    session_scaled:domain_id:period +
    session_scaled:grade:period +
    (1 + session_scaled | user_id),
  control = lmerControl(optCtrl = list(maxfun = 10000)),
  data = multilevel_data_unique)
# does converge
# categorizing individuals based on extended deadline usage improves model

intervention_5 <- lmer(
  q_score_scaled ~ 1 + session_scaled*period +
    session_scaled:difficulty +
    session_scaled:period:ext_deadline_usage +
    period:extended_deadline_group +
    domain_id +
    grade +
    session_scaled:domain_id:period +
    session_scaled:grade:period +
    (1 + session_scaled | user_id),
  control = lmerControl(optCtrl = list(maxfun = 10000)),
  data = multilevel_data_unique)
# does converge
# for some reason, adding both user-specific usage of extended deadline and group categories
# improves the model; however, BIC indicates over-parametrization

intervention_6 <- lmer(
  q_score_scaled ~ 1 + session_scaled*period +
    session_scaled:difficulty +
    session_scaled:period:ext_deadline_usage +
    period:grade:extended_deadline_group +
    domain_id +
    grade + 
    session_scaled:domain_id:period +
    session_scaled:grade:period +
    (1 + session_scaled | user_id),
  control = lmerControl(optCtrl = list(maxfun = 10000)),
  data = multilevel_data_unique)
# does not converge
# adding interaction between grade & extended deadline usage groups leads to issues
# however, removing user-specific usage of extended deadline (the next model) solves this

intervention_final <- lmer(
  q_score_scaled ~ 1 + session_scaled*period +
    session_scaled:difficulty +
    period:grade:extended_deadline_group +
    domain_id +
    grade +
    session_scaled:domain_id:period +
    session_scaled:grade:period +
    (1 + session_scaled | user_id),
  control = lmerControl(optCtrl = list(maxfun = 10000)),
  data = multilevel_data_unique)
# does converge; BIC improvement
# best model thus far

summary(intervention_5)
summary(intervention_final) 
anova(intervention_5, intervention_final)

# Predictions will be made using intervention_final
# Results show that the slope of growth is larger in the period Oct-Dec
# Improvement is most obvious in lower grades, and in domains 7, 9, 10, 11
# Using domain_rating instead of q_score leads to the same results

# Results from intervention_5 are interesting:
# usage of the extended deadline appears to negatively affect q_score
# however, users who use it rarely seem to benefit most from it, showing higher q_scores
# whereas those who use it more often show lower q_scores

# This could simply result from the fact that players who need and use the extended deadline
# are more likely to have less ability than those who do not
```

```{r}
### Preparation for plots & predictions ###

# Custom theme to share across all plots
custom_theme <- theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    legend.position = "bottom",
    legend.title = element_text(face = "bold"),
    legend.text = element_text(size = 10))

# Create a data-frame for SMOOTH (linear) prediction plots (difficulty = 2)
prediction_smooth <- expand.grid(
  session_scaled = seq(min(multilevel_data_unique$session_scaled),
                       max(multilevel_data_unique$session_scaled), length.out = 20),
  period = unique(multilevel_data_unique$period),
  grade = unique(multilevel_data_unique$grade),
  domain_id = unique(multilevel_data_unique$domain_id),
  difficulty = unique(multilevel_data_unique$difficulty),
  extended_deadline_group = unique(multilevel_data_unique$extended_deadline_group),
  user_id = "dummy_user")
  # necessary to include dummy user id, as it's needed for predict() algorithm
  # however, specific user random effects won't be used in making predictions
  # as allow.new.levels = TRUE allows predictions based on fixed effects only

# Set all obs in Sep-Oct to have extended_deadline_group set to "Never"
prediction_smooth <- prediction_smooth %>%
  mutate(extended_deadline_group = ifelse(period == "Sep-Oct", "Never", as.character(extended_deadline_group)))
prediction_smooth$extended_deadline_group <- factor(prediction_smooth$extended_deadline_group, levels = levels(multilevel_data_unique$extended_deadline_group))

# Add predictions to the grid
prediction_smooth$predicted_q_score_scaled <- predict(intervention_final,
                                                      newdata = prediction_smooth,
                                                      allow.new.levels = TRUE)

# De-scale session & q_score for plots
prediction_smooth <- prediction_smooth %>%
  mutate(
    session = session_scaled * session_sd + session_mean,
    predicted_q_score = predicted_q_score_scaled * q_score_sd + q_score_mean
  ) %>%
  select(-predicted_q_score_scaled, -session_scaled)


# Create data-frame for RAW prediction plots
prediction_raw <- multilevel_data_unique
prediction_raw <- prediction_raw %>%
   mutate(predicted_q_score_scaled = predict(intervention_final, newdata = prediction_raw))

# De-scale session & q_score for plots
prediction_raw <- prediction_raw %>%
  mutate(
    session = session_scaled * session_sd + session_mean,
    predicted_q_score = predicted_q_score_scaled * q_score_sd + q_score_mean
  ) %>%
  select(-predicted_q_score_scaled)
```

```{r}
### Plotting slopes for different periods (across domains, grades, difficulties) ###

## SMOOTH PLOT ##
# Aggregate over all other unnecessary variables (for this plot)
prediction_summary_smooth <- prediction_smooth %>%
  group_by(session, period) %>%
  summarize(mean_predicted_q_score = mean(predicted_q_score), .groups = "drop")
prediction_summary_smooth$period <- factor(prediction_summary_smooth$period,
                                           levels = c("Sep-Oct", "Oct-Dec"))

### SMOOTH - Difference in Ability Growth Between the 2 Periods ###
ggplot(prediction_summary_smooth, aes(x = session, y = mean_predicted_q_score, color = period)) +
  geom_line(aes(group = period), size = 1.2) +
  theme_minimal() +
  labs(
    title = "Smooth Model Predictions",
    x = "Session",
    y = "Predicted Q-Score",
    color = "Period"
  ) +
  custom_theme +
  scale_color_manual(values = c("#57b0b5", "#fe6c66"))

## RAW PLOT ##
prediction_summary_raw <- prediction_raw %>%
  group_by(session, period) %>%
  summarize(mean_predicted_q_score = mean(predicted_q_score), .groups = "drop")
prediction_summary_raw$period <- factor(prediction_summary_raw$period,
                                        levels = c("Sep-Oct", "Oct-Dec"))

ggplot(prediction_summary_raw, aes(x = session, y = mean_predicted_q_score, color = period)) +
  geom_line(aes(group = period), size = 1.2) +
  theme_minimal() +
  labs(
    title = "Raw Predictions",
    x = "Session",
    y = "Predicted Q-Score",
    color = "Period"
  ) +
  custom_theme +
  scale_color_manual(values = c("#57b0b5", "#fe6c66"))


## Observed (actual) data plot ##
prediction_summary_obs <- prediction_raw %>%
  group_by(session, period) %>%
  summarize(mean_observed_q_score = mean(q_score), .groups = "drop")
prediction_summary_obs$period <- factor(prediction_summary_obs$period,
                                        levels = c("Sep-Oct", "Oct-Dec"))

ggplot(prediction_summary_obs, aes(x = session, y = mean_observed_q_score, color = period)) +
  geom_line(aes(group = period), size = 1.2) +
  theme_minimal() +
  labs(
    title = "Actual Data",
    x = "Session",
    y = "Observed Q-Score",
    color = "Period"
  ) +
  custom_theme +
  scale_color_manual(values = c("#57b0b5", "#fe6c66"))
```


```{r}
### Plots of growth for different domains ###
domains <- c(1, 2, 3, 4, 5, 7, 9, 10, 11, 59)

## SMOOTH PLOT ##
# Aggregate over all other unnecessary variables
prediction_summary_smooth <- prediction_smooth %>%
  group_by(period, domain_id, session) %>%
  summarize(mean_predicted_q_score = mean(predicted_q_score), .groups = "drop")
prediction_summary_smooth$period <- factor(prediction_summary_smooth$period,
                                           levels = c("Sep-Oct", "Oct-Dec"))

### SMOOTH - Difference in Ability Growth Between the 2 Periods, for all Domains ###
for (i in domains){
  p <- ggplot(prediction_summary_smooth[prediction_summary_smooth$domain_id == i,],
              aes(x = session, y = mean_predicted_q_score, color = period)) +
    geom_line(aes(group = period), size = 1.2) +  # Fit line for each period
    theme_minimal() +
    labs(
      title = paste("Smooth Predicted Session and Q-Score by Period, Domain", i),
      x = "Session",
      y = "Predicted Q-Score",
      color = "Period"
    ) +
    scale_color_manual(values = c("#57b0b5", "#fe6c66")) +
    custom_theme
  print(p)
}

## RAW PLOT ##
prediction_summary_raw <- prediction_raw %>%
  group_by(period, domain_id, session) %>%
  summarize(mean_predicted_q_score = mean(predicted_q_score), .groups = "drop")
prediction_summary_raw$period <- factor(prediction_summary_raw$period, levels = c("Sep-Oct", "Oct-Dec"))

for (i in domains){
  p <- ggplot(prediction_summary_raw[prediction_summary_raw$domain_id == i,],
              aes(x = session, y = mean_predicted_q_score, color = period)) +
    geom_line(aes(group = period), size = 1.2) +  # Fit line for each period
    theme_minimal() +
    labs(
      title = paste("Raw Predicted Session and Q-Score by Period, Domain", i),
      x = "Session",
      y = "Predicted Q-Score",
      color = "Period"
    ) +
    scale_color_manual(values = c("#57b0b5", "#fe6c66")) +
    custom_theme
  print(p)
}


## OBSERVED PLOT ##
prediction_summary_obs <- prediction_raw %>%
  group_by(period, domain_id, session) %>%
  summarize(mean_observed_q_score = mean(q_score), .groups = "drop")
prediction_summary_obs$period <- factor(prediction_summary_obs$period,
                                        levels = c("Sep-Oct", "Oct-Dec"))

for (i in domains){
  p <- ggplot(prediction_summary_obs[prediction_summary_obs$domain_id == i,],
              aes(x = session, y = mean_observed_q_score, color = period)) +
    geom_line(aes(group = period), size = 1.2) +  # Fit line for each period
    theme_minimal() +
    labs(
      title = paste("Observed Session and Q-Score by Period, Domain", i),
      x = "Session",
      y = "Observed Q-Score",
      color = "Period"
    ) +
    scale_color_manual(values = c("#57b0b5", "#fe6c66")) +
    custom_theme
  print(p)
}
```

```{r}
### Difference in Ability Growth Between the 2 Periods, for all Grades ###
grades <- c(3, 4, 5, 6, 7, 8)

## SMOOTH PLOT ##
# Aggregate over all other unnecessary variables
prediction_summary_smooth <- prediction_smooth %>%
  group_by(period, grade, session) %>%
  summarize(mean_predicted_q_score = mean(predicted_q_score), .groups = "drop")
prediction_summary_smooth$period <- factor(prediction_summary_smooth$period,
                                           levels = c("Sep-Oct", "Oct-Dec"))

for (i in grades){
  p <- ggplot(prediction_summary_smooth[prediction_summary_smooth$grade == i,],
              aes(x = session, y = mean_predicted_q_score, color = period)) +
    geom_line(aes(group = period), size = 1.2) +
    theme_minimal() +
    labs(
      title = paste("Smooth Predicted Session and Q-Score by Period, Grade", i),
      x = "Session",
      y = "Predicted Q-Score",
      color = "Period"
    ) +
    scale_color_manual(values = c("#57b0b5", "#fe6c66")) +
    custom_theme
  print(p)
}

## RAW PLOT ##
prediction_summary_raw <- prediction_raw %>%
  group_by(period, grade, session) %>%
  summarize(mean_predicted_q_score = mean(predicted_q_score), .groups = "drop")
prediction_summary_raw$period <- factor(prediction_summary_raw$period,
                                        levels = c("Sep-Oct", "Oct-Dec"))

for (i in grades){
  p <- ggplot(prediction_summary_raw[prediction_summary_raw$grade == i,],
              aes(x = session, y = mean_predicted_q_score, color = period)) +
    geom_line(aes(group = period), size = 1.2) +
    theme_minimal() +
    labs(
      title = paste("Raw Predicted Session and Q-Score by Period, Grade", i),
      x = "Session",
      y = "Predicted Q-Score",
      color = "Period"
    ) +
    scale_color_manual(values = c("#57b0b5", "#fe6c66")) +
    custom_theme
  print(p)
}

## OBSERVED PLOT ##
prediction_summary_obs <- prediction_raw %>%
  group_by(period, grade, session) %>%
  summarize(mean_observed_q_score = mean(q_score), .groups = "drop")
prediction_summary_obs$period <- factor(prediction_summary_obs$period,
                                        levels = c("Sep-Oct", "Oct-Dec"))

for (i in grades){
  p <- ggplot(prediction_summary_obs[prediction_summary_obs$grade == i,],
              aes(x = session, y = mean_observed_q_score, color = period)) +
    geom_line(aes(group = period), size = 1.2) +
    theme_minimal() +
    labs(
      title = paste("Observed Session and Q-Score by Period, Grade", i),
      x = "Session",
      y = "Observed Q-Score",
      color = "Period"
    ) +
    scale_color_manual(values = c("#57b0b5", "#fe6c66")) +
    custom_theme
  print(p)
}
```


```{r}
### Plotting average q_score for different types of users that use the extended deadline ###

## OBSERVED DATA PLOT ##
# results are the same when using predicted q_score values instead of observed ones

# Aggregate over all other unnecessary variables
prediction_summary_raw <- prediction_raw %>%
  filter(period == "Oct-Dec") %>%
  group_by(extended_deadline_group) %>%
  summarize(mean_observed_q_score = mean(q_score), .groups = "drop")

ggplot(prediction_summary_raw, aes(x = extended_deadline_group, y = mean_observed_q_score, color = extended_deadline_group)) +
  geom_point(size = 3, position = position_dodge(width = 0.5)) +  # Mean points
  labs(
    title = "Mean Q-Score by Extended Deadline Usage (Oct-Dec)",
    x = "Extended Deadline Usage",
    y = "Observed Q-score",
    color = "Extended Deadline Usage"
  ) +
  custom_theme +
  theme(legend.position = "none") +
  scale_color_manual(values = c("#008856", "#BE0032", "#0067A5"))
```

```{r}
### Average q_score for different grades & extended deadline usage groupings ###

## OBSERVED DATA PLOT ## 
# results are the same when using predicted q_score values instead of observed ones

# Aggregate over all other unnecessary variables
prediction_summary_raw <- prediction_raw %>%
  filter(period == "Oct-Dec") %>%
  group_by(grade, extended_deadline_group) %>%
  summarize(mean_observed_q_score = mean(q_score),
            mean_predicted_q_score = mean(predicted_q_score), .groups = "drop")

prediction_summary_raw %>%
  ggplot(aes(x = grade, y = mean_observed_q_score, color = extended_deadline_group)) +
  geom_point(size = 1.5) +
  labs(
    title = "Q-Scores by Extended Deadline Usage & Grade (Oct-Dec)",
    x = "Grade",
    y = "Observed Q-score",
    color = "Extended Deadline Usage"
  ) +
  custom_theme +
  scale_color_manual(values = c("green", "red", "blue"))

```


```{r}
oefenwebDatabase::close_connection(con)
```