---
title: "Untitled"
author: "Ender Alexandru, Laura Fetz, Jessee Moomey"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
# Loading packages
library(cowplot)
library(plotly)
library(gridExtra)
library(tidyverse)
library(devtools)
library(oefenwebDatabase)
library(oefenwebTools)
library(lme4)
library(lmerTest)
library(lubridate)
library(DBI)
library(ggalluvial)
# Establishing connection with oefenweb
con <- oefenwebDatabase::connect()
```

Grab the data from original database

```{r}
# Create necessary objects
ed_logs <- list()
domains <- c(1:5, 7, 9, 10, 11, 59)
change_date <- as.Date("2024-10-25")
start_date <- as.Date("2023-09-01")

# Loop through each E_D table
for (i in 1:10) {
  # Write SQL query to get data, and convert to seconds
  query <- paste0("SELECT *
                   FROM extended_deadline_logs_", domains[i])
  # Get the data and store it in the list
  ed_logs[[i]] <- suppressWarnings(DBI::dbGetQuery(con, query))
}

# Turn the list into a single df
ed_logs <- bind_rows(ed_logs)

# Getting deadlines for items in 59
query <- paste0("SELECT id AS item_id,
                 maximum_response_in_seconds AS deadline
                 FROM extended_deadline_items
                 WHERE domain_id = 59")
  # Get the data and store it in the list
deadlines_59 <- suppressWarnings(DBI::dbGetQuery(con, query))

# Convert created to date and into POSIXct format
ed_logs <- ed_logs %>%
  rename(date = created) 
ed_logs$date <-
  as.POSIXct(ed_logs$date, format = "%Y-%m-%d %H:%M:%S")

  
```


```{r}
# Getting item deadlines for domain 59
items_5 <- deadlines_59 %>%
  filter(deadline == 5) %>%
  pull(item_id)

items_10 <- deadlines_59 %>%
  filter(deadline == 10) %>%
  pull(item_id)

items_15 <- deadlines_59 %>%
  filter(deadline == 15) %>%
  pull(item_id)

items_20 <- deadlines_59 %>%
  filter(deadline == 20) %>%
  pull(item_id)

# Categorical columns
cats <- colnames(ed_logs[,c(8:11, 14:15)])

# Adjustments to data
ed_logs = ed_logs %>%
  rename(response_in_seconds = response_in_milliseconds) %>%
  mutate(deadline = case_when(
    domain_id %in% c(1:4, 7, 10) ~ 20,
    domain_id %in% c(9, 11) ~ 30,
    domain_id == 5 ~ 8,
    domain_id == 59 & item_id %in% items_5 ~ 5,
    domain_id == 59 & item_id %in% items_10 ~ 10,
    domain_id == 59 & item_id %in% items_15 ~ 15,
    domain_id == 59 & item_id %in% items_20 ~ 20),
    response_in_seconds = response_in_seconds / 1000,
    across(all_of(cats), as.factor)
  ) 
# Adding time_weeks column and organizing by user_id then date
ed_logs <- ed_logs %>%
  group_by(user_id) %>%
  arrange(user_id, date) %>%
  mutate(time_weeks = ceiling(as.numeric(
    difftime(date, start_date, units = "weeks")
  ))) %>%
  mutate(time_weeks = ifelse(time_weeks < 1, 1, time_weeks)) %>%  # Ensure any negative or 0 values are set to 1
  ungroup() 

```


```{r}
# Total number of unique users
num_users <- n_distinct(ed_logs$user_id)
# 23305

# Finding users that alternate between showing coins and not
swappers <- ed_logs %>%
  select(user_id, show_coins) %>%
  distinct(user_id, show_coins) %>%       # Get unique choices
  count(user_id) %>%                    
  filter(n == 2) %>%                    
  pull(user_id)
# 11118 users have swapped at least once
# Proportion
length(swappers) / num_users # .477065

# Finding users that have never swapped between showing coins or not
not_swappers <- ed_logs %>%
  select(user_id, show_coins) %>%
  distinct(user_id, show_coins) %>%       # Get unique choices
  count(user_id) %>%                    
  filter(n == 1) %>%                    
  pull(user_id)
# 12187 users have never swapped
# Proportion
length(not_swappers) / num_users # .522935

# Users that don't show coins
no_shows <- ed_logs %>%
  distinct(user_id, show_coins) %>%
  filter(user_id %in% not_swappers & show_coins == 0) %>%
  pull(user_id)
# 132 users never showed coins
# Proportion
length(no_shows) / num_users # .005664021

```


```{r}
# Investigating swapping behavior, especially for those swapping to show coins after change

# Getting data needed for sankey plot
sankey_data <- ed_logs %>%
  select(user_id, show_coins, time_weeks) %>%
  filter(user_id %in% swappers) %>%
  mutate(interval = cut(time_weeks, breaks = seq(0, max(time_weeks), by = 2), labels = FALSE))


# Group by individual and interval, then summarize
sankey_tibble <- sankey_data %>%
  group_by(user_id, interval) %>%
  summarize(mode_show_coins = names(which.max(table(show_coins)))) %>%
  ungroup()

# Make the plot
sankey_tibble %>%
ggplot(aes(x = interval, stratum = mode_show_coins, alluvium = user_id, fill = mode_show_coins, label = mode_show_coins)) +
  theme_minimal() +
  #scale_fill_manual(values = color_scheme2) +
  geom_flow(color = "darkgray") +
  geom_stratum() +
  theme(legend.position = "top") +
  labs(x = "2-Week Intervals", y = "Users", title = "Mode show_coins across 2-Week Intervals", legend = "Mode show_coins")
```
Between section 30 and 31 is when the change is made. Which happens to also be paired by a major exodus of students from not showing to then showing, meaning that at least to some extent communication of the feature has occurred outside of personal experience.

```{r}
# Looking deeper. Investigating if students who've never shown coins between sep 1st 2024 and oct 25th 2024 are part of that exodus
stuff <- ed_logs %>%
  select(user_id, show_coins, time_weeks, date) %>%
  filter(user_id %in% swappers, 
         time_weeks %in% 52:64) %>%
  arrange(user_id, time_weeks)

# Users who never showed coins in section 30 where change occurs
unknowners <- stuff %>%
  filter(time_weeks %in% 52:60) %>%    # Keep only rows within the specified weeks
  group_by(user_id) %>%                   # Group by user
  filter(all(show_coins == 0)) %>%        # Keep only users with all 0s across the weeks
  distinct(user_id) %>%
  pull(user_id)

# Users who used coins directly after the change
coiners <- stuff %>%
  group_by(user_id, time_weeks) %>%
  filter(time_weeks %in% 61:62 & any(show_coins == 1)) %>%
  distinct(user_id) %>% 
  pull(user_id)

# Users who went from never showing to showing after the change
enlightened <- stuff %>%
  filter(user_id %in% unknowners & user_id %in% coiners) %>%
  distinct(user_id) %>%
  pull(user_id)

# Proportion of users who went from not showing coins at all before the change, to showing after change
length(enlightened) / length(unknowners) # 0.6403509

```

With over about 64% of users who weren't showing coins changing to showing coins after the change, and showing coins is the only way to see if you're going into extended time, this provides some evidence that communication between students about the extended deadline is likely. However! this could also just be due to students curious about if what changes have been made to the coin animation.

If they now show coins more often than not this could be a sign that it is not initial curiosity, since the coin animation hasn't really changed, but rather is being used as a tool for checking the time, which is evidence of it being knowledge they gained from other students.

```{r}
# Do they show coins more than 1 session
# Count of show_coin setting for never showers who became showers after the change 
show_count <- stuff %>%
  filter(user_id %in% enlightened, time_weeks > 60) %>%
  group_by(user_id, show_coins) %>%
  summarize(count = n(), .groups = "drop") 

# Line chart ordered by proportion of showing coins
show_count %>%
  group_by(user_id) %>%
  mutate(total = sum(count),                         
    prop = sum(count[show_coins == 1]) / total 
  ) %>%
  ungroup() %>%
  mutate(user_id = reorder(user_id, -total, mean)) %>%
  mutate(user_id = reorder(user_id, -prop, mean)) %>% # Reorder by proportion
ggplot(aes(x = user_id, y = count, color = factor(show_coins), group = show_coins)) +
  geom_line() +
  scale_color_manual(values = c("1" = "red", "0" = "blue"),
                     labels = c("Showing", "Not Showing"),
                     name = "Coins") +
  labs(title = "User Coin Showing Behavior", subtitle = "Ordered by Coins Showing / Total Played", x = "Users", y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_blank()) 

```



```{r}
sum(ed_logs$session == "learning_goal")
```



```{r}
oefenwebDatabase::close_connection(con)
```

